\chapter{Tree Graph State}
\label{chap:tree_graph_state}

In this chapter we delve into the critical realm of creating graph states using our qubits.
The work by Y. Zhan \emph{et al.} \cite{tree_graph_state} highlighted the central challenge of reliably transmitting quantum signals through noisy and lossy channels.

While conventional quantum repeater proposals relied on heraled entanglement generation and intricate two-way classical signaling, recent proposals have been made towards leveraging \emph{photonic graph states} to overcome these challenges.
These graph-state-based quantum repeaters present a promising alternative by employing quantum encoding to address photon losses and operational errors, ultimately bypassing the necessity for extensive quantum memory coherence times.

However, generating such photonic graph states traditionally demands substantial resources and intricate methodologies involving linear optics and measurement-based feedforward. 
Despite this challenge, various schemes have been proposed for deterministic generation of these states, including \emph{tree graph} and \emph{repeater graph states}.

Chapter 4 will look into how we can create these graph states using our device. 
In the previous chapter, we figured out the key steps to make specific types of graphs and entanglement bonds between our qubits.
Now, we will use this information to explore ways our device can generate these important graph states for quantum networking.

\input{Chapters/Chapter4/Sec4.1}
\input{Chapters/Chapter4/Sec4.2}